Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-06-03 3dpas_intro.tex
small wording change

Some of the applications we describe are really groups of
applications, meaning that we are grouping together a number of
independent programs, written by different authors, that are trying to
answer the same type of science question and thus, where a single user
will only run one of them at a time.  %\katznote{Shantenu, please check
%the preceding and see if this is ok, in the context of the whole
%paragraph and section.}
These codes and their developers may either be
competing or collaborating, and sometimes both, informally known as
collabetition. Specifically, this is the case for NGS Analytics
(\S\ref{bioSilvia}), SOA Astronomy (\S\ref{astroSOAAdam}), and
Interactive Exploration of Environmental Data (\S\ref{envJon}).  (Note
that this issue is orthogonal to traditional vs. infrastructural applications:
NGS Analytics is traditional, where SOA Astronomy and Interactive
Exploration of Environmental Data are infrastructural.)  In
each of these examples, we have chosen one specific application that
is meant to represent a possibly large number of comparable
applications.

>>>>

Some of the applications we describe are really groups of
applications, meaning that we are grouping together a number of
independent programs, written by different authors, that are trying to
answer the same type of science question, where a single user
will only run one of them at a time.  %\katznote{Shantenu, please check
%the preceding and see if this is ok, in the context of the whole
%paragraph and section.}
These codes and their developers may either be
competing or collaborating, and sometimes both, informally known as
collabetition. Specifically, this is the case for NGS Analytics
(\S\ref{bioSilvia}), SOA Astronomy (\S\ref{astroSOAAdam}), and
Interactive Exploration of Environmental Data (\S\ref{envJon}).  (Note
that this issue is orthogonal to traditional vs. infrastructural applications:
NGS Analytics is traditional, where SOA Astronomy and Interactive
Exploration of Environmental Data are infrastructural.)  In
each of these examples, we have chosen one specific application that
is meant to represent a possibly large number of comparable
applications.
